Implicit yaddayadda

### 2011-08-30 papers/PLDI2012/implicitization.tex
implicitization...

This article makes the following contributions:
\begin{itemize}
\item We improve the technique for obtaining disjunctive invariants from \citet{DBLP:conf/pldi/GulwaniZ10} by replacing the explicit exhaustive enumeration of paths by a sequence of SMT queries.
\item We recast the guided static analysis technique from \citet{DBLP:conf/sas/GopanR07} on the expanded multigraph from \citet{Monniaux_Gonnord_SAS11}, considering entire paths instead of individual transitions, using SMT queries and binary decision diagrams.
\item We implemented these techniques, in addition to ``classical'' iterations and the original guided static analysis, inside a prototype static analyzer.
This tool uses the LLVM bitcode format \cite{Lattner:2004:LCF:977395.977673,LLVM_langref} as input, which can be produced by compilation from C, C++ and Fortran, enabling it to be run on many real-life programs.
With respect to abstract domains on numerical variables, it uses the APRON library \cite{DBLP:conf/cav/JeannetM09}, which supports a variety of abstract domains from which we can choose with minimal changes to our analyzer.
\item We conducted extensive experiments with this tool, on real-life programs, thus obtaining experimental comparisons between the various combinations of techniques.
\end{itemize}

@@

Classical interval analysis on this program yields $\lstinline|x_old| \in [-100000,100000]$.

>>>>

This article makes the following contributions:
\begin{enumerate}
\item We improve the technique for obtaining disjunctive invariants from \citet{DBLP:conf/pldi/GulwaniZ10} by replacing the explicit exhaustive enumeration of paths by a sequence of SMT queries.\label{contr:disjunctive}
\item We recast the guided static analysis technique from \citet{DBLP:conf/sas/GopanR07} on the expanded multigraph from \citet{Monniaux_Gonnord_SAS11}, considering entire paths instead of individual transitions, using SMT queries and binary decision diagrams.\label{contr:guided_multigraph}
\item We implemented these techniques, in addition to ``classical'' iterations and the original guided static analysis, inside a prototype static analyzer.
This tool uses the LLVM bitcode format \cite{Lattner:2004:LCF:977395.977673,LLVM_langref} as input, which can be produced by compilation from C, C++ and Fortran, enabling it to be run on many real-life programs.
With respect to abstract domains on numerical variables, it uses the APRON library \cite{DBLP:conf/cav/JeannetM09}, which supports a variety of abstract domains from which we can choose with minimal changes to our analyzer.
\item We conducted extensive experiments with this tool, on real-life programs, thus obtaining experimental comparisons between the various combinations of techniques.
\end{enumerate}

@@

Classical interval analysis on this program yields $\lstinline|x_old| \in [-100000,100000]$. We have transformed the first program into the second, manually pruning out infeasible paths; yet in general the resulting program could be exponentially larger than the first, even though not all feasible paths are needed to compute the invariant. Following recent suggestions \cite{Gawlitza_Monniaux_ESOP11,Monniaux_Gonnord_SAS11}, we avoid this space explosion by keeping the second program implicit and working from the first program, yet simulating the analysis of the second program. Contribution \ref{contr:disjunctive} (\S\ref{sec:disjunctive}) replaces the exponential expansion of disjunctive invariant generation from \citet{DBLP:conf/pldi/GulwaniZ10} by an implicit representation; contribution \ref{contr:guided_multigraph} (\S\ref{sec:guided_multigraph}) recasts the ``guided analysis'' from \citet{DBLP:conf/sas/GopanR07} on an implicit representation of the paths in lieu of the individual transitions.

\section{Guided widening}
\label{sec:guided_multigraph}

\section{Disjunctive invariants}
\label{sec:disjunctive}

\section{Experimental comparisons}

\section{Conclusion}
